\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-09-21 manuscript.Rmd

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(dev = "png",
                      dpi = 600,
                      echo = FALSE,
                      cache = TRUE)

@@

Our study had four objectives. First, to develop an instrument to assess an individual's light exposure behavior. Second, to conduct an exploratory factor analysis(EFA) to understand the latent structure. The third one is to gather structural validity evidence for the latent structure obtained in EFA. Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017] \# Methods

@@

```{r FlowchartFig, fig.align='center', fig.cap='Development', out.height='100%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/Flowchart1.png')
```

@@

```{r tabDes}
apa_table(Des.combined, caption = "Descriptive Statistics", align = "c", note = "*p<.001", longtable =T)
```

```{r figCor,out.width="50%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}

@@

```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, out.height="100%", out.width="120%"}
knitr::include_graphics('Manuscript.figures/EFAplot.png')

@@

apa_table(factor.des,align = "c", note = "Only loading higher than .30 is reported")
```

```{r Residuals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residulas:  five-factor solution',  out.width="50%",  warning=FALSE}
hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
abline(h =51, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)

@@

```{r tabCfa, results='asis'}
CFa.matrix <- matrix("NA", nrow =2, ncol = 9)
colnames(CFa.matrix) = c("Model", "Chi-Squre", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper CI", "SRMR")
CFa.matrix[1,] = c("Five factor model:25", 
                   apa(cfa.sum.1$FIT[6],2,T), 
                   apa(cfa.sum.1$FIT[7],2,T), 
                   apa(cfa.sum.1$FIT[19],2,F), 
                   apa(cfa.sum.1$FIT[20],2,T),
                   apa(cfa.sum.1$FIT[27],2,T),
                   apa(cfa.sum.1$FIT[28],2,T),
                   apa(cfa.sum.1$FIT[29],2,T),
                   apa(cfa.sum.1$FIT[35],2,T))

CFa.matrix[2,] = c("Five factor model:23", 
                   apa(cfa.sum.2$FIT[6],2,T), 
                   apa(cfa.sum.2$FIT[7],2,T), 
                   apa(cfa.sum.2$FIT[19],2,F), 
                   apa(cfa.sum.2$FIT[20],2,T),
                   apa(cfa.sum.2$FIT[27],2,T),
                   apa(cfa.sum.2$FIT[28],2,T),
                   apa(cfa.sum.2$FIT[29],2,T),
                   apa(cfa.sum.2$FIT[35],2,T))

apa_table(CFa.matrix, caption = "Fit indices of CFA", align = "c", landscape = T)

```{r figcfa, fig.cap = "(A) Five Factor Model of LEBA", , out.width="100%",  warning=FALSE}
#library(semPlot)

@@

```{r InvarianceTab}
apa_table(Invariance.table, align = "c",  caption = "Invariance Analysis", note = " a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "scriptsize" )

@@

## IRT

@@

We combined the EFA and CFA sample (N= 690) and fit each factor of LEBA as a unidimensional construct, and used the graded response model to obtain item parameters(\@ref(tab:IRTparameters). Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Currently, apart from some general suggestions, there exists no definitive rule to judge the item discrimination and item information parameter quality. In this current study, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information \<.2). @bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70. Among the 23 items, 10 items were highly discriminating. Items 16 and 33 had very high discrimination parameters (28.55 & 13.50), indicating their limited applicability to people with a very high level of the latent attribute. Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded.

```{r IRTparameters}
apa_table(itemparameters, caption = "IRT Item parameters for the LEBA Scale", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
```

```{r itminfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10 )

@@

```{r}
F2.redu <- sem.data %>% 
  dplyr::select(item11,  item10 , item12, item7, Ritem8)
F3.redu <- sem.data %>% 
 dplyr::select(item27, item3,  item40)

@@

F5 <- sem.data %>% 
  dplyr::select(item46, item45, item25 )
```

>>>>

@@

Our study had four objectives. First, to develop an instrument to assess an individual's light exposure behavior. Second, to conduct an exploratory factor analysis(EFA) to understand the latent structure. The third one is to gather structural validity evidence for the latent structure obtained in EFA. Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017]

# Methods

@@

```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development', out.height='100%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/Flowchart1.png')
```

@@

```{r tabDes,results='asis'}
apa_table(Des.combined, caption = "Descriptive Statistics", align = "c", note = "*p<.001", longtable =T)
```

```{r figCor,out.width="70%",out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}

@@

```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, out.height="50%", out.width="100%", results='asis'}
knitr::include_graphics('Manuscript.figures/EFAplot.png')

@@

apa_table(factor.des,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading higher than .30 is reported", font_size = "tiny")
```

```{r Residuals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residulas:  five-factor solution',  out.width="50%",  warning=FALSE, results='asis'}
hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
abline(h =51, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)

@@

```{r cfaMat, results='asis'}
CFa.matrix <- matrix("NA", nrow =2, ncol = 9)
colnames(CFa.matrix) = c("Model", "Chi-Squre", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper CI", "SRMR")
CFa.matrix[1,] = c("Five factor model:25", 
                   apa(cfa.sum.1$FIT[6],2,T), 
                   apa(cfa.sum.1$FIT[7],2,T), 
                   apa(cfa.sum.1$FIT[19],2,F), 
                   apa(cfa.sum.1$FIT[20],2,T),
                   apa(cfa.sum.1$FIT[27],2,T),
                   apa(cfa.sum.1$FIT[28],2,T),
                   apa(cfa.sum.1$FIT[29],2,T),
                   apa(cfa.sum.1$FIT[35],2,T))

CFa.matrix[2,] = c("Five factor model:23", 
                   apa(cfa.sum.2$FIT[6],2,T), 
                   apa(cfa.sum.2$FIT[7],2,T), 
                   apa(cfa.sum.2$FIT[19],2,F), 
                   apa(cfa.sum.2$FIT[20],2,T),
                   apa(cfa.sum.2$FIT[27],2,T),
                   apa(cfa.sum.2$FIT[28],2,T),
                   apa(cfa.sum.2$FIT[29],2,T),
                   apa(cfa.sum.2$FIT[35],2,T))
```

```{r tabCfa, results='asis'}
apa_table(CFa.matrix, caption = "Fit indices of CFA", align = "c", landscape = T, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index;RMSEA:Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square ")
```

```{r figcfa, fig.cap = "(A) Five Factor Model of LEBA", , out.width="100%",  warning=FALSE, results='asis'}
#library(semPlot)

@@

```{r InvarianceTab, results='asis'}
apa_table(Invariance.table, align = "c",  caption = "Invariance Analysis", note = " a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "scriptsize" )

@@

## Developing the short form of LEBA

@@

To develop a shorter form of the LEBA we sought to Item response theory.IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty[@bakerBasicsItemResponse2017]. Here, an item’s quality is judged based on item information in relation to participants’ latent trait level ($\theta$). We gathered evidence on item quality  by fitting  each factor of LEBA with the graded response model to the combined EFA sample and CFA sample (n =690)(\@ref(tab:IRTparameters). Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Currently, apart from some general suggestions, there exists no definitive rule to judge the item discrimination and item information parameter quality. Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information \<.2) to develop the short form of LEBA. @bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70. Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), low ( 5 items) indicating  a good range of discrimination along the latent trait. Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded.

```{r IRTparameters, results='asis'}
apa_table(itemparameters, caption = "IRT Item parameters for the LEBA Scale", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
```

```{r itminfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
knitr::include_graphics('Manuscript.figures/Item Informationjpg.jpg')

@@

```{r shortIRT, include=FALSE}
F1 <- sem.data %>% 
  dplyr::select(item16, item36,  item17)
F2.redu <- sem.data %>% 
  dplyr::select(item11,  item10 , item12, item7, Ritem8)
F3.redu <- sem.data %>% 
 dplyr::select(item27, item3,  item40)

@@

F5 <- sem.data %>% 
  dplyr::select(item46, item45, item25 )

F1_fit <- mirt(F1, model = 1, itemtype = 'graded', 
               SE = TRUE, Se.type = 'MHRM',
               technical = list(NCYCLES = 10000))

F2_fit.redu <- mirt(F2.redu, model = 1, itemtype = 'graded', SE = TRUE,
               Se.type = 'MHRM',technical = list(NCYCLES = 10000))

F3_fit.redu <- mirt(F3.redu, model = 1, itemtype = 'graded', SE = TRUE,
               Se.type = 'MHRM',technical = list(NCYCLES = 10000))

F4_fit.redu <- mirt(F4.redu, model = 1, itemtype = 'graded', SE = TRUE,
               Se.type = 'MHRM',technical = list(NCYCLES = 10000))

F5_fit <- mirt(F5, model = 1, itemtype = 'graded', SE = TRUE,
               Se.type = 'MHRM',technical = list(NCYCLES = 10000))

# Plots2 ####

F1_info <- plot(F1_fit, type = "infoSE", main = "Blue Filter")

F2_info.redu <- plot(F2_fit.redu, type = "infoSE", main = "Natural Light Test Information")

F3_info.redu <- plot(F3_fit.redu, type = "infoSE", main = "Smart Device Test Information")

F4_info.redu <- plot(F4_fit.redu, type = "infoSE", main = "Sleep Environment Test Information")

F5_info <- plot(F5_fit, type = "infoSE", main = "Electric Light Test Information")

Test_Info <- plot_grid(F1_info, F2_info.redu,F3_info.redu,F4_info.redu,F5_info, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)

Test information curve (TIC) indicate the amount of information an the full-scale carry along the latent trait continuum. As we treated each factor of LEBA as an unidmensional construct we obtain 5 TICs (). These information curves indicated except Blue filter factor, the other factor's curve is roughly centered on the center of the trait continuum (($\theta$)) and the The amount of information changed rather steadily with the change of ($\theta$).
Thus we conferred the LEBA scale (except blue filter)  estimated the light exposure related behavior with precision near the center of trait continuum [@bakerBasicsItemResponse2017] which is sufficient to discriminate between latent trait measured by the each factor. The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.

```{r fscore, include=FALSE}
LEBA.Total <- sem.data %>% 
  rowwise() %>% 
  mutate(F1.Total = sum(item16, item36,  item17))

LEBA.Total <- LEBA.Total %>% 
  rowwise() %>% 
  mutate(F2.Total = sum(item11,  item10 , item12, item7, Ritem8))

LEBA.Total <- LEBA.Total %>% 
  rowwise() %>% 
  mutate(F3.Total = sum(item27, item3,  item40))

LEBA.Total <- LEBA.Total %>% 
  rowwise() %>% 
  mutate(F4.Total = sum(item32, item35,  item33))

LEBA.Total <- LEBA.Total %>% 
  rowwise() %>% 
  mutate(F5.Total = sum(item46, item45, item25))

F1.estimation <- as.vector(fscores(F1_fit, method = "EAP",
                                           full.scores = TRUE, 
                                           full.scores.SE = F))

F2.estimation <- as.vector(fscores(F2_fit.redu, method = "EAP",
                                           full.scores = TRUE, 
                                           full.scores.SE = F))

F3.estimation <- as.vector(fscores(F3_fit.redu, method = "EAP",
                                           full.scores = TRUE, 
                                           full.scores.SE = F))

F4.estimation <- as.vector(fscores(F4_fit.redu, method = "EAP",
                                           full.scores = TRUE, 
                                           full.scores.SE = F))

F5.estimation <- as.vector(fscores(F5_fit, method = "EAP",
                                           full.scores = TRUE, 
                                           full.scores.SE = F))

Ability.F1 <- data.frame(Rawscore = LEBA.Total$F1.Total,
                      Theta =  F1.estimation)

Ability.F2 <- data.frame(Rawscore = LEBA.Total$F2.Total,
                      Theta =  F2.estimation)

Ability.F3 <- data.frame(Rawscore = LEBA.Total$F3.Total,
                      Theta =  F3.estimation)

Ability.F4 <- data.frame(Rawscore = LEBA.Total$F3.Total,
                      Theta =  F3.estimation)

Ability.F5 <- data.frame(Rawscore = LEBA.Total$F3.Total,
                      Theta =  F3.estimation)

ggplot(Ability.F1, aes(x =Theta, y =Rawscore)) +
  geom_point() +
  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
  xlim(-2,2) +
  ylim(0,15)

ggplot(Ability.F2, aes(x =Theta, y =Rawscore)) +
  geom_point() +
  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
  xlim(-2,2) +
  ylim(0,15)

ggplot(Ability.F3, aes(x =Theta, y =Rawscore)) +
  geom_point() +
  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
  xlim(-2,2) +
  ylim(0,15)

ggplot(Ability.F4, aes(x =Theta, y =Rawscore)) +
  geom_point() +
  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
  xlim(-2,2) +
  ylim(0,15)

ggplot(Ability.F5, aes(x =Theta, y =Rawscore)) +
  geom_point() +
  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
  xlim(-2,2) +
  ylim(0,15)

Score.correation <- cbind(Ability.F1,Ability.F2, Ability.F3, Ability.F4, Ability.F5)
colnames(Score.correation) <- c("F1.Raw", "F1.Estimated","F2.Raw", "F2.Estimated","F3.Raw", "F3.Estimated","F4.Raw", "F4.Estimated","F5.Raw", "F5.Estimated")

F1.cor <- corr.test(Score.correation$F1.Raw, Score.correation$F1.Estimated)

F2.cor <- corr.test(Score.correation$F2.Raw, Score.correation$F2.Estimated)

F3.cor <- corr.test(Score.correation$F3.Raw, Score.correation$F3.Estimated)

F4.cor <- corr.test(Score.correation$F4.Raw, Score.correation$F4.Estimated)

F5.cor <- corr.test(Score.correation$F5.Raw, Score.correation$F5.Estimated)

#Putting significance star for correlation
F1.p <-F1.cor$p
F1.stars <- ifelse(F1.p < .001, "***"
                   , ifelse(p < .01, "**"
                            , ifelse(p < .05, "*"
                                     , ifelse(p < .10, "+", " "))))

F2.p <-F2.cor$p
F2.stars <- ifelse(F2.p < .001, "**"
                   , ifelse(p < .01, "**"
                            , ifelse(p < .05, "*"
                                     , ifelse(p < .10, "+", " "))))

F3.p <-F3.cor$p
F3.stars <- ifelse(F3.p < .001, "***"
                   , ifelse(p < .01, "**"
                            , ifelse(p < .05, "*"
                                     , ifelse(p < .10, "+", " "))))

F4.p <-F4.cor$p
F4.stars <- ifelse(F4.p < .001, "***"
                   , ifelse(p < .01, "**"
                            , ifelse(p < .05, "*"
                                     , ifelse(p < .10, "+", " "))))

F5.p <-F5.cor$p
F5.stars <- ifelse(F5.p < .001, "***"
                   , ifelse(p < .01, "**"
                            , ifelse(p < .05, "*"
                                     , ifelse(p < .10, "+", " "))))

theta.correlation.matrix <- matrix("NA", nrow =1, ncol = 5)

theta.correlation.matrix[1,1] <- paste(apa(F1.cor$r,2,F), F1.stars,sep="")
theta.correlation.matrix[1,2] <- paste(apa(F2.cor$r,2,F), F2.stars,sep="")
theta.correlation.matrix[1,3] <- paste(apa(F3.cor$r,2,F), F3.stars,sep="")
theta.correlation.matrix[1,4] <- paste(apa(F4.cor$r,2,F), F4.stars,sep="")
theta.correlation.matrix[1,5] <- paste(apa(F5.cor$r,2,F), F5.stars,sep="")

as.data.frame(theta.correlation.matrix)
colnames(theta.correlation.matrix) <- c("F1", "F2", "F3", "F4", "F5")
```

```{r, results='asis'}
apa_table (theta.correlation.matrix, caption = "correlation coefficents of obtained scores and estimated latent trait for each factots", note = "* p < 0.05; ** p < 0.01; *** p < 0.001"  )
```
